### 2014-04-15 HW_non-modal.tex
April 14

Turbulence in magnetically confined plasmas is almost always attributed to linear instabilities. The calculation of linear instabilities through normal mode analysis
-- the calculation of eigenvalues and eigenvectors of a linearized dynamical system -- has successfully predicted the onset criterion for many MHD and micro-instabilities.
Nevertheless, it is well-known in the hydrodynamics community that normal mode analysis fails at predicting turbulent onset for a large class of experiments that are deemed to have
subcritical turbulence. Subcritical turbulence is certainly possible in plasmas, and several instances have been studied in the 
past~\cite{waltz1985,scott1990,scott1992,nordman1993,biskamp1995,drake1995,camargo1998,krommes1999,scott2002,camporeale2009,camporeale2010,schekochihin2012,highcock2012}. 
For the most part, however, normal mode analysis dominates plasma turbulence prediction despite the fact that it is not useful in all instances.

Since the hydrodynamics community has long studied subcritical turbulence, it has much to offer in terms of understanding the phenomenon. Most significantly,
in the early 1990's, Trefethen and others attributed the failure of normal mode analysis in predicting subcritical turbulent onset to the non-normality of linear operators of
dynamical systems~\cite{trefethen1993,schmid2007}. A non-normal operator has 
eigenvectors that are not orthogonal to one another. One consequence of eigenvector nonorthogonality is that even when all eigenvectors decay exponentially under linear evolution, 
superpositions of eigenvectors can grow, albeit transiently.
In other words, certain fluctuations of the laminar state can access free energy from background gradients even though normal mode fluctuations cannot.
When combined with nonlinear effects, this allows for sustained subcritical turbulence by a bootstrapping process.
Such behavior is obscured by traditional normal mode analysis, which only effectively describes the long time asymptotic behavior of fluctuations under  
action of the linear operator. Transient growth, which can dominate turbulent evolution, can be discovered only through non-modal calculations.

Non-modal analysis generally employs tools such as pseudospectra and maximum possible transient growth curves, which have been used to successfully explain why turbulence is subcritical in various
systems. However, to our knowledge, they have not been used to predict onset criteria in subcritical systems (e.g. the transition Reynold's number in pipe flows), although non-normal
turbulent arguments have been applied in generating amplitude versus Reynold's number scalings for turbulent onset.
This paper takes up the task of developing a new approach to understand turbulent properties using only non-modal linear calculations with the goal of 
ultimately making quantitative predictions.  Our approach is to calculate an average growth rate of turbulent fluctuations due to linear processes, specifically due to transient growth.  We model the
turbulent steady state as a series of processes:  (1) the turbulence starts as a spatially random state, (2) linear transient growth deterministically amplifies the turbulent energy (or
decrease it in wavenumber ranges where linear damping dominates), (3) nonlinear transfer sets in at a specified timescale, terminating the
transient growth process and re-randomizing the turbulent state (at which point the cycle repeats).    Optimally, the timescale for the final step would be the
nonlinear decorrelation time of the turbulent system, but in order to enable predictive capability, we employ critical balance
arguments to use a characteristic \emph{linear} time. The procedure ultimately produces a growth rate that can be used
to predict turbulent properties such as saturation levels and transport rates through mixing length arguments.

@@

In the analysis and numerical simulations, which we perform with the BOUT++ code~\cite{dudson2009}, we use periodic boundary conditions in
the $y$ and $z$ directions with zero-value boundaries in the $x$ direction. We use a domain size of $64 \rho_s \times 64 rho_s \times 300 \rho_s$.
For the 2D version of the model, we replace $-\xi \gradpar^2$ by $\alpha = k_z^2 \xi = 4 \pi k_z^2 \rho_s^2 \omega_{ce} /\nu_{ei}$, 
which is commonly known as the adiabaticity parameter~\cite{camargo1995,camargo1998}. Additionally we use a domain size of $50 \rho_s \times 50 \rho_s$.
In numerical simulations, the turbulence can laminarize due to the build-up of $k_y=0$ density and potential structures~\cite{biskamp1995}. To prevent this, we subtract out the $k_y=0$
$n$ and $\phi$ components, which is the equivalent of adding source terms to Eqs.~\ref{n_eq} and~\ref{phi_eq}~\cite{friedman2012b}.

@@

\beqar
\label{fourier_en_eqn}
\frac{\partial}{\partial t} \left( \begin{array}{cc} n_k \\ k_\perp \phi_k \end{array} \right) = \mathbf{B}_k \left( \begin{array}{cc} n_k \\ k_\perp \phi_k \end{array} \right) + \mathbf{N}_k \left( \begin{array}{cc} n_k \\ k_\perp \phi_k \end{array} \right), \\ \nonumber \\
\label{B_k}
\mathbf{B}_k = \left( \begin{array}{cc} -\xi k_z^2 - D k_\perp^4 & -i \kappa \frac{k_y}{k_\perp} + \xi \frac{k_z^2}{k_\perp} \\  \xi \frac{k_z^2}{k_\perp} & - \xi \frac{k_z^2}{k_\perp^2} - D k_\perp^4\end{array} \right)
\eeqar
Since the square $L_2$-norm of the new state vector $\frac{1}{\sqrt{2}} \left( \begin{array}{cc} n_k \\ k_\perp \phi_k \end{array} \right)$ gives the energy contained in the mode $k$,
$\mathbf{B}_k$ is the energetically-weighted matrix of interest. In the limit of large $\xi k_z^2$ as long as $k_\perp$ is also not too large:

@@

Linear non-normality is important for the effect it has on turbulence. It is most often cited as the sufficient condition for turbulence in subcritical systems, 
but it can also impact systems that have unstable linear eigenmodes like the HW system. Since certain superpositions of the linear eigenmodes can inject energy faster than the most unstable linear
eigenmode, there is the possibility that the energy injection into the turbulence is faster and at different wavenumbers than is suggested by linear eigenmode analysis. 
To understand this concept and show that it occurs in the nonlinear HW model, we compare the fastest growing linear eigenmode growth rate $\gamma_{s,k}$ to the turbulent growth rate $\gamma_{t,k}$. 
To define the turbulent growth rate in general and specifically for the HW model, we employ a Fourier-decomposed energy dynamics analysis~\cite{camargo1995,friedman2012b,friedman2013}. 
To do this, we take Eqs.~\ref{n_eq} and~\ref{phi_eq} and substitute the following:

@@

Although the instability is a nonlinear instability, the first part of the mechanism -- the transport of background density by the convective cells -- is a linear one.
Biskamp and Drake understood this and wondered how there could be linear energy injection despite the fact that the linear eigenvectors are stable.
The answer to this came when Camargo et al.~\cite{camargo1998} stated that ``some properties of the drift-wave turbulence
previously attributed to nonlinear terms could also be strongly influenced by the nonnormal character of the linear system.'' Although Camargo et al. focused only on the 2D HW model,
based on this statement, it was likely apparent to them that the 3D HW nonlinear instability was a result of linear non-normality. 
Therefore, when $k_z=0$, no matter the value of $\xi$, the adiabaticity parameter $\alpha = k_z^2 \xi = 0$, meaning the linear matrix operator is highly non-normal and subject to transient growth.
So non-normal effects plays a role in the 3D HW system no matter what value of $\xi$ is chosen due to the presence of $k_z=0$ structures.

@@

In this section, we outline a procedure that uses quick and simple methods to approximate the turbulent growth rates $\gamma_{t,k}$.
We contend that the key to doing this is to successfully model the effect that the nonlinearities have on the linear (modal and transient) processes.
First, we note that the advective nonlinearity terms in Eqs.~\ref{n_eq} and~\ref{phi_eq} have the form of the state variable divided by a time $\tau_{nl} \sim (v_E k_\perp)^{-1}$. 
This nonlinear time scale is generally associated with the eddy turnover or decorrelation time. We therefore present a heuristic model of the nonlinearities 
as a randomizing force that acts on this characteristic nonlinear time scale. More specifically, this model is one in which 1) the turbulence begins as a random state, 
2) evolves linearly for a time $\tau_{nl}$, and 3) randomizes by nonlinear energy transfer, at which point the steps repeat.

This model can be used by starting with an ensemble of random initial conditions, evolving them linearly for a time $\tau_{nl}$, and
then taking the time and ensemble averaged growth rate of these curves.
In practice, this procedure can be greatly sped up and simplified. To see this, recall that the time evolution of the energy from an initial condition is

\beq
\label{E_t_from_u0}
E_k(t) = ||e^{\mathbf{B}_k t} u(0)||^2 = e^{\mathbf{B}_k t} u(0) u^{\dagger}(0) e^{\mathbf{B}_k^{\dagger}t}.
\eeq
Since we want to take the $\mathbf{u}(0)$ in the ensemble as random normalized vectors with uncorrelated components, it follows that~\cite{camargo1998}

\beq
\label{E_t_ensemble_avg}
\left< E_k(t) \right>_{{\rm{ens}}} = \frac{1}{2} {\rm{tr}} \{ e^{\mathbf{B}_k t} e^{\mathbf{B}^{\dagger}t} \},
\eeq
where the normalization is $||\mathbf{u}(0)||^2 = 1$. Mathematically, we define the non-modal growth rate $\gamma_{{\rm{nm}},k}$ as the time averaged instantaneous growth rate:

\beq
\label{gamma_nm_calc}
\gamma_{{\rm{nm}},k} = \frac{1}{\tau_{nl,k}} \int_0^{\tau_{nl,k}} \frac{\pdiff{E_k(t)}{t}}{2 E_k(t)} dt = \frac{1}{2 \tau_{nl,k}} \ {\rm{Log}} \left[ \frac{E_k(\tau_{nl,k})}{E_k(0)}\right].
\eeq
Next, we substitute the ensemble averaged energy calculated from Eq.~\ref{E_t_ensemble_avg} for $E_k(t)$, and set $E_k(0) = 1$ by our normalization. Then,

\beq
\label{gamma_nm}
\gamma_{{\rm{nm}},k} = \frac{1}{2 \tau_{nl,k}} \ {\rm{Log}} \left<  E_k(\tau_{nl,k}) \right>_{\rm{ens}}
\eeq
Now, in order to obtain a simple and quick prediction of $\gamma_{{\rm{nm}},k}$, we must estimate $\tau_{nl,k}$ without having to calculate it directly from a simulation. 
We thus invoke the conjecture of \emph{critical balance}, which posits that the nonlinear time scale equals the linear time scale at all spatial scales~\cite{schekochihin2012}. This is a fair
assumption in light of our discussion above, in which we derived the relation: $\gamma_{l,k} = - \gamma_{nl,k}$.

@@

We test both of these non-modal growth rates to see if either or both produce good approximations of $\gamma_{t,k}$, especially in comparison to $\gamma_{s,k}$. 
In Fig.~\ref{alpha1e-5_gamma_spec_compare}, we show the $\gamma_{\omega,k}$ and $\gamma_{\gamma,k}$ spectra for the 2D HW
model for $\alpha=10^{-5}$ along with the eigenmode and turbulent spectra ($\gamma_{s,k}$ and $\gamma_{t,k}$), which we already provided in Fig.~\ref{alpha1e-5_gamma_s_t}. We do the same for
$\alpha=1$ in Fig.~\ref{alpha1_gamma_s_t}. For the highly non-normal case ($\alpha = 10^{-5}$), $\gamma_{\omega,k}$ reproduces $\gamma_{t,k}$ in both magnitude and spectral shape. $\gamma_{\gamma,k}$
is not close in any respect to $\gamma_{t,k}$. On the other hand, for the nearly normal case ($\alpha=1$), $\gamma_{\omega,k}$ does not resemble $\gamma_{t,k}$. $\gamma_{\gamma,k}$ actually is
fairly similar to $\gamma_{s,k}$, but with a slightly decreased amplitude, making it a closer match to $\gamma_{t,k}$, though it is still not similar for all $k$.

@@

We further test how well the maxima of the non-modal growth rates predict the maxima of the turbulent growth rates. We show the result in Fig.~\ref{gamma_max_with_nm}. For $\alpha < 10^{-3}$,
in which the system is fairly non-normal, $\gamma_{\omega,k}$ predicts $\gamma_{t,k}$ quite accurately. As the system becomes more normal, $\gamma_{t,k}$ and $\gamma_{\omega,k}$ diverge, with
$\gamma_{t,k}$ taking on values between $\gamma_{s,k}$ and $\gamma_{\omega,k}$, but generally closer to $\gamma_{s,k}$ for $\alpha \gg 10^{-3}$. 
This indicates that some assumption in our procedure doesn't work well for systems that are normal or nearly normal. Namely, our assumption
of complete randomization by the nonlinearities breaks down. Apparently, the nonlinearities only partially randomize the turbulence. For the most part, the turbulence at a given $k$ consists
primarily of the unstable eigenmode, while the stable eigenmode accounts for only a small amount of energy in the turbulence. Finally, $\gamma_{\gamma,k}$ is not useful in predicting $\gamma_{t,k}$.
It is closest to $\gamma_{t,k}$ for $\alpha \ge 1$, however, it only provides a slight improvement over $\gamma_{s,k}$ in this range.

@@

The lower curve represents the second kind of subcritical system. Above a critical value of the control parameter $R_c$, the system is linearly unstable. But, for $R_g < R < R_c$, the system is
unstable to finite amplitude perturbations, or ``nonlinearly'' unstable. A paradigmatic example of this is Poissuille channel flow -- the rectangular analog of pipe flow -- for which
$R_c = 5772$ and $R_g \approx 1000$~\cite{grossmann2000}. Most subcritical magnetically-confined plasma systems fall into this category. It is perhaps easy to be fooled into believing that the turbulence
in such systems is due to eigenmode instability. In either case, one of the most important predictions is the minimum turbulent control parameter $R_g$.

@@

>>>>

Turbulence in magnetically confined plasmas is almost always attributed to linear instabilities. The calculation of linear instabilities through normal mode analysis
-- the calculation of eigenvalues and eigenvectors of a linearized dynamical system -- has successfully predicted the onset criterion for many MHD and micro-instabilities.
Nevertheless, it is well-known in the hydrodynamics community that normal mode analysis fails at predicting turbulent onset for a large class of experiments, in which the
turbulence is called subcritical. In these experiments, turbulence appears even though all linear eigenvectors are stable, meaning infinitesimal perturbations on the laminar state cannot grow
exponentially. Nevertheless, finite amplitude perturbations can still excite turbulence.
Subcritical turbulence is certainly possible in plasmas as well, and several instances have been studied in the 
past~\cite{waltz1985,scott1990,scott1992,nordman1993,biskamp1995,drake1995,camargo1998,krommes1999,scott2002,camporeale2009,camporeale2010,schekochihin2012,highcock2012}. 
For the most part, however, normal mode analysis dominates plasma turbulence prediction despite the fact that it is not useful in all instances.

Since the hydrodynamics community has long studied subcritical turbulence, it has much to offer in terms of understanding of the phenomenon. Most significantly,
in the early 1990s, Trefethen and others attributed the failure of normal mode analysis in predicting subcritical turbulent onset to the non-normality of linear operators of
dynamical systems~\cite{trefethen1993,schmid2007}. A non-normal operator has 
eigenvectors that are not orthogonal to one another. One consequence of eigenvector nonorthogonality is that even when all eigenvectors decay exponentially under linear evolution, 
superpositions of eigenvectors can grow, albeit transiently.
In other words, certain fluctuations of the laminar state can access free energy from background gradients even though normal mode fluctuations cannot.
When combined with nonlinear effects, this allows for sustained subcritical turbulence by a bootstrapping process.
Such behavior is obscured by traditional normal mode analysis, which only effectively describes the long time asymptotic behavior of fluctuations under  
action of the linear operator. Transient growth, which can dominate turbulent evolution, can be discovered only through non-modal calculations.

Non-modal analysis generally employs tools such as pseudospectra and maximum possible transient growth curves, which have been used to successfully explain why turbulence is subcritical in various
systems. However, they have not been used to predict onset criteria in subcritical systems (e.g. the transition Reynold's number in pipe flows), although non-normal
turbulent arguments have been applied in generating amplitude versus Reynold's number scalings for turbulent onset~\cite{grossmann2000}.
This paper takes up the task of developing a new approach to understand turbulent properties using only non-modal linear calculations with the goal of 
ultimately making quantitative predictions.  Our approach is to calculate an average growth rate of turbulent fluctuations due to linear processes, specifically due to transient growth.  We model the
turbulent steady state as a series of processes:  (1) the turbulence starts as a spatially random state, (2) linear transient growth deterministically amplifies the turbulent energy (or
decrease it in wavenumber ranges where linear damping dominates), (3) nonlinear transfer sets in at a specified timescale, terminating the
transient growth process and re-randomizing the turbulent state (at which point the cycle repeats).    Optimally, the timescale for the final step would be the
nonlinear decorrelation time of the turbulent system, but in order to enable predictive capability, we employ critical balance
arguments to use a characteristic \emph{linear} time. The procedure ultimately produces a growth rate that can be used
to predict turbulent properties such as saturation levels and transport rates through mixing length arguments.

@@

In the analysis and numerical simulations, which we perform with the BOUT++ code~\cite{dudson2009}, we use periodic boundary conditions in
the $y$ and $z$ directions with zero-value boundaries in the $x$ direction. We use a domain size of $64 \rho_s \times 64 \rho_s \times 300 \rho_s$.
For the 2D version of the model, we replace $-\xi \gradpar^2$ by $\alpha (= k_z^2 \xi = 4 \pi k_z^2 \rho_s^2 \omega_{ce} /\nu_{ei})$, 
which is commonly known as the adiabaticity parameter~\cite{camargo1995,camargo1998}. Additionally we use a domain size of $50 \rho_s \times 50 \rho_s$.
In numerical simulations, the turbulence can laminarize due to the build-up of $k_y=0$ density and potential structures~\cite{biskamp1995}. To prevent this, we subtract out the $k_y=0$
$n$ and $\phi$ components, which is the equivalent of adding source terms to Eqs.~\ref{n_eq} and~\ref{phi_eq}~\cite{friedman2012b}.

@@

\beqar
\label{fourier_en_eqn}
\frac{\partial}{\partial t} \left( \begin{array}{cc} n_k \\ k_\perp \phi_k \end{array} \right) = \mathbf{B}_k \left( \begin{array}{cc} n_k \\ k_\perp \phi_k \end{array} \right) + \mathbf{N}_k \left( \begin{array}{cc} n_k \\ k_\perp \phi_k \end{array} \right), \\ \nonumber \\
\label{B_k}
\mathbf{B}_k = \left( \begin{array}{cc} -\xi k_z^2 - D k_\perp^4 & -i \kappa \frac{k_y}{k_\perp} + \xi \frac{k_z^2}{k_\perp} \\  \xi \frac{k_z^2}{k_\perp} & - \xi \frac{k_z^2}{k_\perp^2} - D k_\perp^4\end{array} \right)
\eeqar
Since the square $L_2$-norm of the new state vector $\frac{1}{\sqrt{2}} \left( \begin{array}{cc} n_k \\ k_\perp \phi_k \end{array} \right)$ gives the energy contained in the mode $k$,
$\mathbf{B}_k$ is the energetically-weighted matrix of interest. In the limit of large $\xi k_z^2$ (as long as $k_\perp$ is also not too large):

@@

Linear non-normality is important for the effect it has on turbulence. It is most often cited as a necessary condition for turbulence in subcritical systems. 
But it can also impact systems that have unstable linear eigenmodes like the HW system. Since certain superpositions of the linear eigenmodes can inject energy faster than the most unstable linear
eigenmode, there is the possibility that the energy injection into the turbulence is faster and at different wavenumbers than is suggested by linear eigenmode analysis. 
To understand this concept and show that it occurs in the nonlinear HW model, we compare the fastest growing linear eigenmode growth rate $\gamma_{s,k}$ to the turbulent growth rate $\gamma_{t,k}$. 
To define the turbulent growth rate in general and specifically for the HW model, we employ a Fourier-decomposed energy dynamics analysis~\cite{camargo1995,friedman2012b,friedman2013}. 
To do this, we take Eqs.~\ref{n_eq} and~\ref{phi_eq} and substitute the following:

@@

Although the instability is a nonlinear instability, the first part of the mechanism -- the transport of background density by the convective cells -- is a linear one.
Biskamp and Drake understood this and wondered how there could be linear energy injection despite the fact that the linear eigenvectors are stable.
The answer to this came when Camargo et al.~\cite{camargo1998} stated that ``some properties of the drift-wave turbulence
previously attributed to nonlinear terms could also be strongly influenced by the nonnormal character of the linear system.'' Although Camargo et al. focused only on the 2D HW model,
based on this statement, it was likely apparent to them that the 3D HW nonlinear instability was a result of linear non-normality. 
Therefore, when $k_z=0$, no matter the value of $\xi$, the adiabaticity parameter $\alpha = k_z^2 \xi = 0$, meaning the linear matrix operator is highly non-normal and subject to transient growth.
So non-normal effects play a role in the 3D HW system for all $\xi$ due to the presence of $k_z=0$ structures.

@@

In this section, we outline a procedure that uses quick and simple methods to approximate the turbulent growth rates $\gamma_{t,k}$.
We contend that the key to doing this is to successfully model the effect that the nonlinearities have on the linear (modal and transient) processes.
First, we note that the advective nonlinearity terms in Eqs.~\ref{n_eq} and~\ref{phi_eq} have a common form -- a state variable multiplied by an inverse time scale:
$\tau_{nl}^{-1} \sim v_E k_\perp$.
This nonlinear time scale is generally associated with the eddy turnover or decorrelation time. We thus present a heuristic model of the nonlinearities 
as a randomizing force that acts on this characteristic nonlinear time scale. More specifically, this model is one in which 1) the turbulence begins as a random state, 
2) evolves linearly for a time $\tau_{nl}$, and 3) randomizes by nonlinear energy transfer, at which point the steps repeat.

We can calculate an effective growth rate from this model by starting with an ensemble of random initial conditions, evolving them linearly for a time $\tau_{nl}$, and
then taking the time and ensemble averaged growth rate of these curves.
In practice, this procedure can be greatly sped up and simplified. To see this, recall that the time evolution of the energy from an initial condition is

\beq
\label{E_t_from_u0}
E_k(t) = ||e^{\mathbf{B}_k t} u(0)||^2 = e^{\mathbf{B}_k t} u(0) u^{\dagger}(0) e^{\mathbf{B}_k^{\dagger}t}.
\eeq
Since we want the ensemble of initial conditions ($u(0)$'s) to be random normalized vectors with uncorrelated components, it follows that~\cite{camargo1998}

\beq
\label{E_t_ensemble_avg}
\left< E_k(t) \right>_{{\rm{ens}}} = \frac{1}{2} {\rm{tr}} \{ e^{\mathbf{B}_k t} e^{\mathbf{B}^{\dagger}t} \},
\eeq
where the normalization is $||u(0)||^2 = 1$. Mathematically, we define the non-modal growth rate $\gamma_{{\rm{nm}},k}$ as the time averaged instantaneous growth rate:

\beq
\label{gamma_nm_calc}
\gamma_{{\rm{nm}},k} = \frac{1}{\tau_{nl,k}} \int_0^{\tau_{nl,k}} \frac{\pdiff{E_k(t)}{t}}{2 E_k(t)} dt = \frac{1}{2 \tau_{nl,k}} \ {\rm{Log}} \left[ \frac{E_k(\tau_{nl,k})}{E_k(0)}\right].
\eeq
Taking $E_k(t)$ as the ensemble averaged energy calculated from Eq.~\ref{E_t_ensemble_avg} and set $E_k(0) = 1$ for normalization, we find,

\beq
\label{gamma_nm}
\gamma_{{\rm{nm}},k} = \frac{1}{2 \tau_{nl,k}} \ {\rm{Log}} \left<  E_k(\tau_{nl,k}) \right>_{\rm{ens}}
\eeq
Now, in order to obtain a simple and quick prediction of $\gamma_{{\rm{nm}},k}$, we must estimate $\tau_{nl,k}$ without having to calculate it directly from a turbulent simulation. 
We thus invoke the conjecture of \emph{critical balance}, which posits that the nonlinear time scale equals a characteristic linear time scale at all spatial scales~\cite{schekochihin2012}. 
This is a fair assumption in light of our discussion above, in which we showed that $\gamma_{l,k} = - \gamma_{nl,k}$.

@@

We test both of these non-modal growth rates to see if either or both produce good approximations of $\gamma_{t,k}$, especially in comparison to $\gamma_{s,k}$. 
In Fig.~\ref{alpha1e-5_gamma_spec_compare}, we show the $\gamma_{\omega,k}$ and $\gamma_{\gamma,k}$ spectra for the 2D HW
model for $\alpha=10^{-5}$ along with the eigenmode and turbulent spectra ($\gamma_{s,k}$ and $\gamma_{t,k}$), which we already provided in Fig.~\ref{alpha1e-5_gamma_s_t}. We do the same for
$\alpha=1$ in Fig.~\ref{alpha1_gamma_spec_compare}. For the highly non-normal case ($\alpha = 10^{-5}$), $\gamma_{\omega,k}$ reproduces $\gamma_{t,k}$ in both magnitude and spectral shape. 
$\gamma_{\gamma,k}$ is not close in any respect to $\gamma_{t,k}$. On the other hand, for the nearly normal case ($\alpha=1$), $\gamma_{\omega,k}$ does not resemble $\gamma_{t,k}$. 
$\gamma_{\gamma,k}$ actually is fairly similar to $\gamma_{s,k}$, but with a slightly decreased amplitude, making it a closer match to $\gamma_{t,k}$, though it is still not similar for all $k$.

@@

We further test how well the maxima of the non-modal growth rates predict the maxima of the turbulent growth rates. We show the result in Fig.~\ref{gamma_max_with_nm}. For $\alpha \le 10^{-4}$,
in which the system is fairly non-normal, $\gamma_{\omega,k}$ predicts $\gamma_{t,k}$ quite accurately. As the system becomes more normal, $\gamma_{t,k}$ and $\gamma_{\omega,k}$ diverge, with
$\gamma_{t,k}$ taking on values between $\gamma_{s,k}$ and $\gamma_{\omega,k}$, but generally closer to $\gamma_{s,k}$ for $\alpha \gg 10^{-3}$. 
This indicates that some assumption in our procedure doesn't work well for systems that are normal or nearly normal. Namely, our assumption
of complete randomization by the nonlinearities breaks down. Apparently, the nonlinearities only partially randomize the turbulence. For the most part, the turbulence at a given $k$ consists
primarily of the unstable eigenmode, while the stable eigenmode accounts for only a small amount of energy in the turbulence. Finally, $\gamma_{\gamma,k}$ is not useful in predicting $\gamma_{t,k}$.
It is closest to $\gamma_{t,k}$ for $\alpha \ge 1$, however, it only provides a slight improvement over $\gamma_{s,k}$ in this range.

@@

The lower curve represents the second kind of subcritical system. Above a critical value of the control parameter $R_c$, the system is linearly unstable. But, for $R_g < R < R_c$, the system is
unstable to finite amplitude perturbations, or ``nonlinearly'' unstable. A paradigmatic example of this is Poissuille channel flow -- the rectangular analog of pipe flow -- for which
$R_c = 5772$ and $R_g \approx 1000$~\cite{grossmann2000}. Most subcritical magnetically-confined plasma systems fall into this category. It is perhaps easy to be fooled into believing that the turbulence
in such systems is due to eigenmode instability. In either case, one of the most important predictions is the minimum turbulent control parameter $R_g$. Given that this problem is many decades old
and still unsolved, it is a tall order to predict $R_g$ without nonlinear simulations. We nevertheless make an attempt.

@@

\begin{figure}
\centerline{\includegraphics[width=0.4\textwidth]{kappa_en_ev}}
\caption{}
\label{kappa_en_ev}
\end{figure}
